### 2014-03-08 src/analysis.Rnw
update

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------

>>>>

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of one element selection, All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------
<<oth>>=
stats.o <- stats.rest
o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.o) <- new.colnames
colnames(r.stats.sel.o) <- new.colnames

@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Others}
\label{tbl:osel}
\end{table*}

% ----------------------------------------------------------------------
